---
title: "Untitled"
author: "Dylan Berneman"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
install.packages("plotrix")
library(plotrix)
library(ggplot2)
library(lubridate)
install.packages("ggrepel")
library(ggrepel)
library(readxl)
```

```{r}

Monthly_Data <- read_excel("Project 2 Historical Data.xlsx", 
    sheet = "60-40 Returns Monthly", range = "B10:D1174")

Monthly_Data1 <- read_excel("Project 2 Historical Data.xlsx", 
    sheet = "60-40 Returns Monthly", range = "B10:D1174")

Monthly_Data1 = Monthly_Data
Monthly_Data1[c(2,3)] = 1 + Monthly_Data1[c(2,3)] 

vect0 = vector()
for(i in 0:100){
  vect0 = append(vect0, paste0("Folio ", i, "/",100-i))
}

Monthly_Data2 = Monthly_Data1
Monthly_Data3 = Monthly_Data1

# 12-month returns
for(i in 1:805){
  x=i
  y=x+359
  Monthly_Data1$`Large Cap TR`[i] = prod(Monthly_Data1$`Large Cap TR`[x:y])-1
  Monthly_Data1$FIXED[i] = prod(Monthly_Data1$FIXED[x:y])-1
  Monthly_Data2$`Large Cap TR`[i] = sum(Monthly_Data2$`Large Cap TR`[x:y])/360 - 1
  Monthly_Data2$FIXED[i] = sum(Monthly_Data2$FIXED[x:y])/360 - 1
  Monthly_Data3$`Large Cap TR`[i] = prod(Monthly_Data3$`Large Cap TR`[x:y])^(1/360)-1
  Monthly_Data3$FIXED[i] = prod(Monthly_Data3$FIXED[x:y])^(1/360)-1}






# 12-month allocation returns
for(i in 0:100){
  alpha = i/100
  Monthly_Data1[paste0("Folio", i)] = NA
  Monthly_Data2[paste0("Folio", i)] = NA
  Monthly_Data3[paste0("Folio", i)] = NA
  for(j in 1:805){
    Monthly_Data1[j, i+4] = alpha*Monthly_Data1$`Large Cap TR`[j] + (1-alpha)*Monthly_Data1$FIXED[j]
    Monthly_Data2[j, i+4] = alpha*Monthly_Data2$`Large Cap TR`[j] + (1-alpha)*Monthly_Data2$FIXED[j]
    Monthly_Data3[j, i+4] = alpha*Monthly_Data3$`Large Cap TR`[j] + (1-alpha)*Monthly_Data3$FIXED[j]
    }}
Monthly_Data1 = Monthly_Data1[,4:104]
Monthly_Data2 = Monthly_Data2[,4:104]
Monthly_Data3 = Monthly_Data3[,4:104]



Monthly_Data1 = Monthly_Data1[1:805,]
Monthly_Data2 = Monthly_Data2[1:805,]
Monthly_Data3 = Monthly_Data3[1:805,]

Monthly_Data1 = Monthly_Data1^(1/36)-1
Monthly_Data2 = (1+Monthly_Data2)^(12)-1
Monthly_Data3 = (1+Monthly_Data3)^(12)-1


stat = Monthly_Data1[1:101, 1:8]
stat[,1:8]=NA
colnames(stat) = c("Allocation", "Num", "Compound_Mean", "Compound_std", "Arith_Mean", "Arith_std", "Geom_Mean", "Geom_std")
stat$Allocation = colnames(Monthly_Data1)[1:101]
stat["Num"] = c(seq(0,100,1))



for(i in 0:100){
  stat[i+1, 3] = sum(Monthly_Data1[, i+1])/805
  stat[i+1, 4] = sqrt(var(Monthly_Data1[, i+1]))
  stat[i+1, 5] = sum(Monthly_Data1[, i+1])/805
  stat[i+1, 6] = sqrt(var(Monthly_Data2[, i+1]))
  stat[i+1, 7] = sum(Monthly_Data3[, i+1])/805
  stat[i+1, 8] = sqrt(var(Monthly_Data3[, i+1]))}

Allocation = vector()
for(i in 0:100){
  Allocation = append(Allocation, paste0("Large Cap = ", i, "%, Fixed = ", 100-i, "%"))}
stat$Allocation = c(Allocation)

stat$Allocation = factor(stat$Allocation, levels = c(stat$Allocation))



for(i in c(4,6,8)){
  frame = stat[,  c(1:2, i, i-1)]
  min1 = min(frame[,3])
  max1 = max(frame[,3])
  min2 = min(frame[,4])
  max2 = max(frame[,4])
  vect = vector()
  vect = append(vect, c(1,61,101))
  for(j in 1:101){
    if((frame[j, 3] == min1) | (frame[j, 3] == max1)){
      vect = append(vect, frame$Num[j+1])}
    if((frame[j, 4] == min2) | (frame[j, 4] == max2)){
      vect = append(vect, frame$Num[j+1])}}
  vect = unique(vect)
  vect = sort(vect)
  signif_pts = stat[c(vect), c(1:2, i, i-1)]
  signif_pts = signif_pts %>%
    mutate("Rank" = rank(signif_pts[,3]))
  signif_pts["Rank_Color"] = NA
  vect_col = vector()
  if(length(vect)==5){
    for(k in 1:length(vect)){
      if(as.integer(signif_pts$Rank[k]) == 1){
        vect_col = append(vect_col, "green")}
      else{
        if(as.integer(signif_pts$Rank[k]) == 2){
          vect_col = append(vect_col, "greenyellow")}
        else{
          if(as.integer(signif_pts$Rank[k]) == 3){
            vect_col = append(vect_col, "yellow")}
          else{
            if(as.integer(signif_pts$Rank[k]) == 4){
              vect_col = append(vect_col, "orange")}
            else{
              if(as.integer(signif_pts$Rank[k]) == 5){
                vect_col = append(vect_col, "red")}}}}}}}
  if(length(vect)==4){
    for(k in 1:length(vect)){
      if(as.integer(signif_pts$Rank[k]) == 1){
        vect_col = append(vect_col, "green")}
      else{
        if(as.integer(signif_pts$Rank[k]) == 2){
          vect_col = append(vect_col, "yellow")}
        else{
          if(as.integer(signif_pts$Rank[k]) == 3){
            vect_col = append(vect_col, "orange")}
          else{
            if(as.integer(signif_pts$Rank[k]) == 4){
              vect_col = append(vect_col, "red")}}}}}}
  if(length(vect)==3){
    for(k in 1:length(vect)){
      if(as.integer(signif_pts$Rank[k]) == 1){
        vect_col = append(vect_col, "green")}
      else{
        if(as.integer(signif_pts$Rank[k]) == 2){
          vect_col = append(vect_col, "orange")}
        else{
          if(as.integer(signif_pts$Rank[k]) == 3){
            vect_col = append(vect_col, "red")}}}}}
  signif_pts$Rank_Color = vect_col
  signif_pts["Type"] = colnames(signif_pts)[3]
  colnames(signif_pts)[3:4] = c("STD", "Mean")
  assign(paste0("signif1_", colnames(frame)[3]), signif_pts)}


signif_pts_all = rbind(signif1_Compound_std, signif1_Arith_std, signif1_Geom_std)



# significant_Losses_FIXa %>%
#   ggplot()+
#   geom_col(aes(x=abs(FIX60), y = Month, fill = Probability)) +
#   facet_wrap(~as.character(Year)) +
#   labs(title="12-Month Significant Losses on the Blended Fixed Income Fund for the 60/40 Portfolio",
#   x = "Investment Loss")+
#   scale_fill_manual(values  = c("< 5%" = "yellow",
#                                 "< 1%" = "orange",
#                                 "< 0.1%" = "orangered1")) +
#   geom_text(aes(x = abs(FIX60), y = Month, label = round(abs(FIX60), 4)), hjust=1) +
#   theme(plot.title = element_text(hjust = 0.5),
#         strip.text = element_text(size = 15),
#         axis.text = element_text(size = 12),
#         axis.title = element_text(size = 15),
#         title =element_text(size=18, face='bold'),
#         legend.text = element_text(size = 12))

name = "Compound"
name1 = "Arithmetic"
name2 = "Geometric"

df1 = stat[,c(1,2,3,4)]
colnames(df1)[3:4] = c("Mean", "Std")
df1$Allocation = paste0(name, ":", "\n", df1$Allocation)
df1["Type"] = "Compound"
df2 = stat[,c(1,2,5,6)]
colnames(df2)[3:4] = c("Mean", "Std")
df2$Allocation = paste0(name1, ":", "\n", df2$Allocation)
df2["Type"] = "Arith"
df3 = stat[,c(1,2,7,8)]
colnames(df3)[3:4] = c("Mean", "Std")
df3$Allocation = paste0(name2, ":", "\n", df3$Allocation)
df3["Type"] = "Geom"
stata = rbind(df1,df2,df3)


for(i in 1:12){
  if(signif_pts_all$Rank[i] == 1){
    signif_pts_all$Shape[i] = 15}
  if(signif_pts_all$Rank[i] == 2){
    signif_pts_all$Shape[i] = 16}
  if(signif_pts_all$Rank[i] == 3){
    signif_pts_all$Shape[i] = 17}
  if(signif_pts_all$Rank[i] == 4){
    signif_pts_all$Shape[i] = 18}
  
}


stata$Type = factor(stata$Type)

signif_pts_all["Shape"] = c(rep(15, 4), rep(16, 4), rep(17, 4))
# signif_pts_all$Allocation = factor(signif_pts_all$Allocation)
# signif_pts_all$Rank_Color = factor(signif_pts_all$Rank_Color)

signif_pts0 = signif_pts_all
col_pal <- c(signif_pts0$Rank_Color)
shape_pal <- c(signif_pts0$Shape)
ggplot(data = stata, aes(x= Std, y = Mean, facet = Type)) + geom_point() +
  geom_label(data=signif_pts0[c(3,7,11),], aes(x = STD, y = Mean, 
                                   label = paste0(
                                     "Mean: ", signif(Mean, 4), "\n", 
                                     "SD: ", signif(STD, 4))),
             color = "darkgreen", size=4, nudge_x = 0.001) + 
  geom_point(data = signif_pts0, aes(x = STD, y = Mean, color=Allocation, shape = Allocation), size=5)+
  scale_color_manual(values = col_pal) +
  scale_shape_manual(values = shape_pal) +
  labs(title = "Arithmetic 30 Year Average Returns: \n Mean vs. Standard Deviation") +
  ylab("Mean") +
  xlab("Standard Deviation") +
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.75, 0.75),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15))

signif_pts0 = signif1_Compound_std
col_pal <- c(signif_pts0$Rank_Color)
ggplot(data = stat, aes(x= Compound_std, y = Compound_Mean)) + geom_point() +
  geom_label(data=signif_pts0[3,], aes(x = STD, y = Mean, 
                                   label = paste0(
                                     "Mean: ", signif(Mean, 4), "\n", 
                                     "SD: ", signif(STD, 4))),
             color = "darkgreen", size=4, nudge_x = 0.001) + 
  geom_point(data=signif_pts0, aes(color=Allocation), size=5)+
  scale_color_manual(values = col_pal[1:4]) +
  labs(title = "Arithmetic 30 Year Average Returns: \n Mean vs. Standard Deviation") +
  ylab("Mean") +
  xlab("Standard Deviation") +
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.75, 0.75),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15))







# geom_point(data = stat, aes(x = Arith_std, y = Arith_Mean)) + 
#   geom_label(data=signif_pts_all[3,], aes(x = Arith_std, y = Arith_Mean, 
#                                    label = paste0(
#                                      "Mean: ", signif(Arith_Mean, 4), "\n", 
#                                      "SD: ", signif(Arith_std, 4))),
#              color = "darkgreen", size=4, nudge_x = 0.00015) +
#   geom_point(data = signif_pts1, aes(color = Allocation), size=5)
# 
# signif_pt = rbind(signif_pts0, signif_pts1, signif_pts2, na.)
# 
# 
# + 
#   geom_point(data = signif_pts1, aes(color=Allocation), size=5)+
#   geom_point(data = stat, aes(x = Geom_std, y = Geom_Mean)) + 
#   geom_label(data=signif_pts0[3,], aes(x = Geom_std, y = Geom_Mean, 
#                                    label = paste0(
#                                      "Mean: ", signif(Geom_Mean, 4), "\n", 
#                                      "SD: ", signif(Geom_std, 4))),
#              color = "darkgreen", size=4, nudge_x = 0.00015) + 
#   geom_point(data = signif_pts2, aes(color=Allocation), size=5)+
# `
```





# 30 yr arithmetic mean vs std
signif_pts0 = signif_pts_all
col_pal <- c(signif_pts0$Rank_Color)
ggplot(data = stata, aes(x= Std, y = Mean, fill = Type)) + geom_point() +
  geom_label(data=signif1_Compound_std [3,], aes(x = STD, y = Mean, 
                                   label = paste0(
                                     "Mean: ", signif(Mean, 4), "\n", 
                                     "SD: ", signif(STD, 4))),
             color = "darkgreen", size=4, nudge_x = 0.00015) + 
  geom_point(data = signif_pts_all, aes(x = STD, y = Mean, color=Allocation, shape = Type), size=5)+
  geom_label(data=signif1_Arith_std [3,], aes(x = STD, y = Mean, 
                                   label = paste0(
                                     "Mean: ", signif(Mean, 4), "\n", 
                                     "SD: ", signif(STD, 4))),
             color = "darkgreen", size=4, nudge_x = 0.00015) + 
  geom_point(data = signif1_Arith_std, aes(x = STD, y = Mean, color=Allocation), size=5)+
  geom_label(data=signif1_Geom_std [3,], aes(x = STD, y = Mean, 
                                   label = paste0(
                                     "Mean: ", signif(Mean, 4), "\n", 
                                     "SD: ", signif(STD, 4))),
             color = "darkgreen", size=4, nudge_x = 0.00015) + 
  geom_point(data = signif1_Geom_std, aes(x = STD, y = Mean, color=Allocation), size=5)+
  scale_color_manual(values = col_pal)+
  labs(title = "Arithmetic 30 Year Average Returns: \n Mean vs. Standard Deviation") +
  ylab("Mean") +
  xlab("Standard Deviation") +
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.75, 0.75),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15))



```{r}

# # Annual Allocation returns
# for(i in 0:100){
#   alpha = i/100
#   Data[paste0("Folio", i)] = NA
#   for(j in 1:97){
#     Data[j, length(colnames(Data))] = alpha*Data$LCTR_true[j] + (1-alpha)*Data$FIXED_true[j]}}

# Annual from Monthly
annual = data.frame(matrix(ncol=102,nrow=97))
colnames(annual) = colnames(Monthly_Data)[c(1, 4:104)]
x=1
for(i in 1:1153){
  if((i-1)%%12 ==0){
    annual[x,] = Monthly_Data[i,c(1,4:104)]
    annual[x,1] = year(Monthly_Data$Date[i])
    x = x + 1}}

# IB
IB <- read_excel("Project 2 Historical Data.xlsx",
    range = "AO11:AR1175", col_types = c("numeric",
        "skip", "skip", "numeric"))

IB["Date"] = Monthly_Data1$Date 
IB = IB[,c(3,1:2)]
IB_plus1 = IB


IB[,2:3] = 1 + IB[,2:3]
IB2 = IB
IB3 = IB


colnames(IB) = c("Date", "t_bill", "inflation")
IB_Monthly_cmp12 = IB
IB_Monthly_cmp12 = IB_Monthly_cmp12[1:1153,]
IB_Monthly_cmp12[,2:3]=NA
for(j in 2:3){
  for(i in 1:1153){
    x=i
    y1=x+11
    IB_Monthly_cmp12[i,j] = prod(IB_plus1[x:y1, j])-1}}

IB_annual_cmp12 = IB_Monthly_cmp12[1:97,]
x=1
for(i in 1:1153){
  if((i-1)%%12==0){
    IB_annual_cmp12[x,] = IB_Monthly_cmp12[i,]
    x=x+1}}

Annual_IB_Data_a = IB_annual_cmp12
colnames(Annual_IB_Data_a) = colnames(IB_annual_cmp12)
Annual_IB_Data_g = Annual_IB_Data_a

# Mean
Mean = annual
colnames(Mean)[2:102] = vect0
Mean1 = Mean
Mean1[,2:102] = Mean1[,2:102]+1
arith = Mean[1:68,]
# arith mean
arith[, c(2:102)] = NA
# arith sharpe
arith1 = arith
arith11 = arith
# arith risk reward ratio
arith_rrr = arith
# geom mean
Geom = arith
# geom sharpe
Geom1 = arith
Geom11 = arith
# geom risk reward ratio
Geom_rrr = arith

IB_annual_cmp12_g = IB_annual_cmp12
IB_annual_cmp12_g[,2:3] = 1 + IB_annual_cmp12_g[,2:3]

for(i in 1:2){
  for(j in 1:68){
    x=j
    y=x+29
    Annual_IB_Data_a[j, i+1] = sum(IB_annual_cmp12[x:y, i+1])/30
    Annual_IB_Data_g[j, i+1] = prod(IB_annual_cmp12_g[x:y, i+1])^(1/30)-1}}

Annual_IB_Data_a = Annual_IB_Data_a %>%
  mutate("diff" = Annual_IB_Data_a$t_bill - Annual_IB_Data_a$inflation)

Annual_IB_Data_g = Annual_IB_Data_g %>%
  mutate("diff" = Annual_IB_Data_g$t_bill - Annual_IB_Data_g$inflation)

for(i in 0:100){
  for(j in 1:68){
    x=j
    y=x+29
    arith[j,i+2] = mean(Mean[x:y, i+2])
    Geom[j,i+2] = (prod(Mean1[x:y, i+2]))^(1/30)-1}}


arith_CI = arith
Geom_CI = Geom

for(i in 0:100){
  for(j in 1:68){
    x=j
    y=x+29
    std = sqrt(var(Mean[x:y, i+2]))
    name = paste0("CI", i)
    arith_CI[j, i+2] = arith[j, i+2] - 1.96*std
    arith_rrr[j, i+2] = std/arith[j, i+2]
    arith1[j, i+2] = arith[j, i+2] - Annual_IB_Data_a$diff[j]
    arith1[j, i+2] = arith1[j, i+2]/std
    arith11[j, i+2] = arith[j, i+2] - Annual_IB_Data_a$t_bill[j]
    arith11[j, i+2] = arith11[j, i+2]/std
    Geom_CI[j, i+2] = Geom[j, i+2] - 1.96*std
    Geom_rrr[j, i+2] = std/Geom[j, i+2]
    Geom1[j, i+2] = Geom[j, i+2] - Annual_IB_Data_g$diff[j]
    Geom1[j, i+2] = Geom1[j, i+2]
    Geom11[j, i+2] = Geom[j, i+2] - Annual_IB_Data_g$t_bill[j]
    Geom11[j, i+2] = Geom11[j, i+2]/std}}




total = Mean1
total = total[1:68,]
total[,2:102]=NA
total_rrr = total
total_sharpe1 = total
total_sharpe2 = total
for(i in 0:100){
  for(j in 1:68){
    x=j
    y=x+29
    std = sd(Mean1[x:y, i+2])
    total[j,i+2] = (prod(Mean1[x:y, i+2]))
    total_sharpe1[j,i+2] = (((prod(Mean1[x:y, i+2])) - prod(IB_plus1[x:y, 2]) + prod(IB_plus1[x:y, 3]))/std)^(1/30)
    total_sharpe2[j,i+2] = (((prod(Mean1[x:y, i+2])) - prod(IB_plus1[x:y, 2]))/std)^(1/30)
    total_rrr[j,i+2]= (total[j,i+2]/std)^(1/30)}}

stats = data.frame(matrix(nrow=101, ncol = 26))
colnames(stats) = c("Allocation", "Spread_num", "arith_Mean", "arith_STD_DEV", "arith_Sharpe1", "arith_Sharpe1_std", "arith_Sharpe2", "arith_Sharpe2_std", "arith_RRR",  "arith_RRR_std", "Geom_Mean", "Geom_STD_DEV", "Geom_Sharpe1", "Geom_Sharpe1_std", "Geom_Sharpe2", "Geom_Sharpe2_std", "Geom_RRR",  "Geom_RRR_std", "Total_Return", "Total_Return_std", "Total_Sharpe1", "Total_Sharpe1_std", "Total_Sharpe2", "Total_Sharpe2_std", "Total_RRR", "Total_RRR_std")
stats$Spread_num = c(seq(0,100,1))
Allocation = vector()
for(i in 0:100){
  Allocation = append(Allocation, paste0("Large Cap = ", i, "%, Fixed = ", 100-i, "%"))}
stats$Allocation = c(Allocation)

# Stats
for(i in 0:100){
  stats$arith_Mean[i+1] = sum(arith[,i+2])/68
  stats$arith_STD_DEV[i+1] = sqrt(var(arith[, i+2]))
  stats$arith_Sharpe1[i+1] = sum(arith1[,i+2])/68
  stats$arith_Sharpe2[i+1] = sum(arith11[,i+2])/68
  stats$arith_Sharpe1_std[i+1] = sqrt(var(arith1[,i+2]))
  stats$arith_Sharpe2_std[i+1] = sqrt(var(arith11[,i+2]))
  stats$arith_RRR[i+1] = sum(arith_rrr[,i+2])/68
  stats$arith_RRR_std[i+1] = sqrt(var(arith_rrr[,i+2]))
  stats$Geom_Mean[i+1] = sum(Geom[,i+2])/68
  stats$Geom_STD_DEV[i+1] = sqrt(var(Geom[, i+2]))
  stats$Geom_Sharpe1[i+1] = sum(Geom1[,i+2])/68
  stats$Geom_Sharpe2[i+1] = sum(Geom11[,i+2])/68
  stats$Geom_Sharpe1_std[i+1] = sqrt(var(Geom1[,i+2]))
  stats$Geom_Sharpe2_std[i+1] = sqrt(var(Geom11[,i+2]))
  stats$Geom_RRR[i+1] = sum(Geom_rrr[,i+2])/68
  stats$Geom_RRR_std[i+1] = sqrt(var(Geom_rrr[,i+2]))
  stats$Total_Return[i+1] = sum(total[, i+2])/68
  stats$Total_Return_std[i+1] = sqrt(var(total[, i+2]))
  stats$Total_RRR[i+1] = sum(total_rrr[, i+2])/68
  stats$Total_RRR_std[i+1] = sqrt(var(total_rrr[, i+2]))
  stats$Total_Sharpe1[i+1] = sum(total_sharpe1[, i+2])/68
  stats$Total_Sharpe1_std[i+1] = sqrt(var(total_sharpe1[, i+2]))
  stats$Total_Sharpe2[i+1] = sum(total_sharpe2[, i+2])/68
  stats$Total_Sharpe2_std[i+1] = sqrt(var(total_sharpe2[, i+2]))}


stats2 = data.frame(matrix(nrow=101, ncol = 28))
colnames(stats2) = c("Allocation", "Spread_num", "arith_CI", "arith_CI2", "arith_Sharpe1_CI", "arith_Sharpe1_CI2", "arith_Sharpe2_CI", "arith_Sharpe2_CI2", "arith_RRR_CI", "arith_RRR_CI2", "Geom_CI", "Geom_CI2", "Geom_Sharpe1_CI", "Geom_Sharpe1_CI2", "Geom_Sharpe2_CI", "Geom_Sharpe2_CI2", "Geom_RRR_CI", "Geom_RRR_CI2", "Total_Return_CI", "Total_Return_CI2", "Total_Sharpe1_CI", "Total_Sharpe1_CI2", "Total_Sharpe2_CI", "Total_Sharpe2_CI2", "Total_RRR_CI", "Total_RRR_CI2", "Prob", "Prob2")
stats2[,1:2] = stats[, 1:2]

# Stats
for(i in 0:100){
  stats2$arith_CI[i+1] = stats$arith_Mean[i+1] - 1.96 * stats$arith_STD_DEV[i+1]
  stats2$arith_CI2[i+1] = stats$arith_Mean[i+1] + 1.96 * stats$arith_STD_DEV[i+1]
  stats2$arith_Sharpe1_CI[i+1] = stats$arith_Sharpe1[i+1] - 1.96 * stats$arith_Sharpe1_std[i+1]
  stats2$arith_Sharpe1_CI2[i+1] = stats$arith_Sharpe1[i+1] + 1.96 * stats$arith_Sharpe1_std[i+1]
  stats2$arith_Sharpe2_CI[i+1] = stats$arith_Sharpe2[i+1] - 1.96 * stats$arith_Sharpe2_std[i+1]
  stats2$arith_Sharpe2_CI2[i+1] = stats$arith_Sharpe2[i+1] + 1.96 * stats$arith_Sharpe2_std[i+1]
  stats2$arith_RRR_CI[i+1] = stats$arith_RRR[i+1] - 1.96 * stats$arith_RRR_std[i+1]
  stats2$arith_RRR_CI2[i+1] = stats$arith_RRR[i+1] + 1.96 * stats$arith_RRR_std[i+1]
  stats2$Geom_CI[i+1] = stats$Geom_Mean[i+1] - 1.96 * stats$Geom_STD_DEV[i+1]
  stats2$Geom_CI2[i+1] = stats$Geom_Mean[i+1] + 1.96 * stats$Geom_STD_DEV[i+1]
  stats2$Geom_Sharpe1_CI[i+1] = stats$Geom_Sharpe1[i+1] - 1.96 * stats$Geom_Sharpe1_std[i+1]
  stats2$Geom_Sharpe1_CI2[i+1] = stats$Geom_Sharpe1[i+1] + 1.96 * stats$Geom_Sharpe1_std[i+1]
  stats2$Geom_Sharpe2_CI[i+1] = stats$Geom_Sharpe2[i+1] - 1.96 * stats$Geom_Sharpe2_std[i+1]
  stats2$Geom_Sharpe2_CI2[i+1] = stats$Geom_Sharpe2[i+1] + 1.96 * stats$Geom_Sharpe2_std[i+1]
  stats2$Geom_RRR_CI[i+1] = stats$Geom_RRR[i+1] - 1.96 * stats$Geom_RRR_std[i+1]
  stats2$Geom_RRR_CI2[i+1] = stats$Geom_RRR[i+1] + 1.96 * stats$Geom_RRR_std[i+1]
  stats2$Total_Return_CI[i+1] = stats$Total_Return[i+1] - 1.96 * stats$Total_Return_std[i+1]
  stats2$Total_Return_CI2[i+1] = stats$Total_Return[i+1] + 1.96 * stats$Total_Return_std[i+1]
  stats2$Total_RRR_CI[i+1] = stats$Total_RRR[i+1] - 1.96 * stats$Total_RRR_std[i+1]
  stats2$Total_RRR_CI2[i+1] = stats$Total_RRR[i+1] + 1.96 * stats$Total_RRR_std[i+1]
  stats2$Total_Sharpe1_CI[i+1] = stats$Total_Sharpe1[i+1] - 1.96 * stats$Total_Sharpe1_std[i+1]
  stats2$Total_Sharpe1_CI2[i+1] = stats$Total_Sharpe1[i+1] + 1.96 * stats$Total_Sharpe1_std[i+1]
  stats2$Total_Sharpe2_CI[i+1] = stats$Total_Sharpe2[i+1] - 1.96 * stats$Total_Sharpe2_std[i+1]
  stats2$Total_Sharpe2_CI2[i+1] = stats$Total_Sharpe2[i+1] + 1.96 * stats$Total_Sharpe2_std[i+1]
  stats2[i+1,27] = pnorm(1, mean = stats$arith_RRR[i+1], sd = stats$arith_RRR_std[i+1], lower.tail = TRUE)
  stats2[i+1,28] = pnorm(1, mean = stats$Geom_RRR[i+1], sd = stats$Geom_RRR_std[i+1], lower.tail = TRUE)}

stats2$Allocation = factor(stats2$Allocation, levels = c(stats2$Allocation))
stats$Allocation = factor(stats$Allocation, levels = c(stats$Allocation))

pnorm(0.1, lower.tail = FALSE)

```

```{r}
for(i  in c(4,6,8,10,12,14,16,18,20,22,24,26)){
  frame = stats[,  c(1,2, i, i-1)]
  min = min(frame[,3])
  max = max(frame[,3])
  vect = vector()
  vect = append(vect, c(1,61,101))
  for(j in 1:101){
    if((frame[j, 3] == min) | (frame[j, 3] == max)){
      vect = append(vect, frame[j+1, 2])}}
  vect = unique(vect)
  if(i==14){
    vect = append(vect, 32)}
  if(i==16){
    vect = append(vect, 69)}
  if(i==20){
    vect = append(vect, 90)} 
  if(i==24){
    vect = append(vect, 78)} 
  if(i==26){
    vect = append(vect, 83)} 
  if(i==22){
    vect = append(vect, 12)}
  vect = sort(vect)
  signif_pts = stats[c(vect), c(1,2, i, i-1)]
  signif_pts = signif_pts %>%
    mutate("Rank" = rank(signif_pts[,3]))
  signif_pts["Rank_Color"] = NA
  vect_col = vector()
  if(length(vect)==5){
    for(k in 1:length(vect)){
      if(as.integer(signif_pts$Rank[k]) == 1){
        vect_col = append(vect_col, "green")}
      else{
        if(as.integer(signif_pts$Rank[k]) == 2){
          vect_col = append(vect_col, "greenyellow")}
        else{
          if(as.integer(signif_pts$Rank[k]) == 3){
            vect_col = append(vect_col, "yellow")}
          else{
            if(as.integer(signif_pts$Rank[k]) == 4){
              vect_col = append(vect_col, "orange")}
            else{
              if(as.integer(signif_pts$Rank[k]) == 5){
                vect_col = append(vect_col, "red")}}}}}}}
  if(length(vect)==4){
    for(k in 1:length(vect)){
      if(as.integer(signif_pts$Rank[k]) == 1){
        vect_col = append(vect_col, "green")}
      else{
        if(as.integer(signif_pts$Rank[k]) == 2){
          vect_col = append(vect_col, "yellow")}
        else{
          if(as.integer(signif_pts$Rank[k]) == 3){
            vect_col = append(vect_col, "orange")}
          else{
            if(as.integer(signif_pts$Rank[k]) == 4){
              vect_col = append(vect_col, "red")}}}}}}
  if(length(vect)==3){
    for(k in 1:length(vect)){
      if(as.integer(signif_pts$Rank[k]) == 1){
        vect_col = append(vect_col, "green")}
      else{
        if(as.integer(signif_pts$Rank[k]) == 2){
          vect_col = append(vect_col, "orange")}
        else{
          if(as.integer(signif_pts$Rank[k]) == 3){
            vect_col = append(vect_col, "red")}}}}}
  signif_pts$Rank_Color = vect_col
  assign(paste0("signif1_", colnames(frame)[3]), signif_pts)}


for(i in c(3,5,7,9,11,13,15,17,19,21,23,25,27,28)){
  if(i!=27 & i!=28){
    frame = stats2[,  c(1,2, i, i+1)]}
  if(i==27 | i==28){
    frame = stats2[, c(1,2, i)]}
  min = min(frame[,3])
  max = max(frame[,3])
  vect = vector()
  vect = append(vect, c(1,61,101))
  if(i==3){
    vect = append(vect, 81)}
  if(i==11){
    vect = append(vect, 78)}
  if(i==23){
    vect = append(vect, 20)}
  if(i==25){
    vect = append(vect, 77)}
  if(i==25){
    vect = append(vect, 77)}
  if(i==21){
    vect = append(vect, 18)}
  for(j in 1:101){
    if((frame[j, 3] == min) | (frame[j, 3] == max)){
      vect = append(vect, frame[j+1, 2])}}
  vect = unique(vect)
  vect = sort(vect)
  if(i!=27 & i!=28){
    signif_pts = stats2[c(vect), c(1,2, i, i+1)]}
  if(i==27 | i==28){
    signif_pts = stats2[c(vect), c(1,2, i)]}
  if(i==9 | i==17 | i==21){
    signif_pts = signif_pts %>%
      mutate("Rank" = rank(signif_pts[,3]))}
  if(i!=9 & i !=17 & i!=21){
    if(length(vect)==3){
      signif_pts = signif_pts %>%
        mutate("Rank" = 4-rank(signif_pts[,3]))}
    else{
      if(length(vect)==4){
        signif_pts = signif_pts %>%
          mutate("Rank" = 5-rank(signif_pts[,3]))}
      else{
      if(length(vect)==5){
        signif_pts = signif_pts %>%
          mutate("Rank" = 6-rank(signif_pts[,3]))}}}}
  signif_pts["Rank_Color"] = NA
  vect_col = vector()
  if(length(vect)==5){
    for(k in 1:length(vect)){
      if(as.integer(signif_pts$Rank[k]) == 1){
        vect_col = append(vect_col, "green")}
      else{
        if(as.integer(signif_pts$Rank[k]) == 2){
          vect_col = append(vect_col, "greenyellow")}
        else{
          if(as.integer(signif_pts$Rank[k]) == 3){
            vect_col = append(vect_col, "yellow")}
          else{
            if(as.integer(signif_pts$Rank[k]) == 4){
              vect_col = append(vect_col, "orange")}
            else{
              if(as.integer(signif_pts$Rank[k]) == 5){
                vect_col = append(vect_col, "red")}}}}}}}
  if(length(vect)==4){
    for(k in 1:length(vect)){
      if(as.integer(signif_pts$Rank[k]) == 1){
        vect_col = append(vect_col, "green")}
      else{
        if(as.integer(signif_pts$Rank[k]) == 2){
          vect_col = append(vect_col, "yellow")}
        else{
          if(as.integer(signif_pts$Rank[k]) == 3){
            vect_col = append(vect_col, "orange")}
          else{
            if(as.integer(signif_pts$Rank[k]) == 4){
              vect_col = append(vect_col, "red")}}}}}}
  if(length(vect)==3){
    for(k in 1:length(vect)){
      if(as.integer(signif_pts$Rank[k]) == 1){
        vect_col = append(vect_col, "green")}
      else{
        if(as.integer(signif_pts$Rank[k]) == 2){
          vect_col = append(vect_col, "orange")}
        else{
          if(as.integer(signif_pts$Rank[k]) == 3){
            vect_col = append(vect_col, "red")}}}}}
  signif_pts$Rank_Color = vect_col
  assign(paste0("signif_", colnames(frame)[3]), signif_pts)}
```


```{r}
# 30 yr arithmetic CI
signif_pts0 = signif_arith_CI
col_pal <- c(signif_pts0$Rank_Color)
ggplot(data = stats2, aes(x = Spread_num, y = arith_CI)) + 
  geom_point() + 
  geom_label(data=signif_pts0[4,], aes(x = Spread_num, y = arith_CI, 
                                   label = paste0(
                                     "95% CI:", "\n", "[", round(arith_CI, 4), ", ", 
                                     round(arith_CI2, 4),"]")),
             color = "darkgreen", size=4, nudge_y = -0.01, nudge_x = -6) + 
  geom_point(data = signif_pts0, aes(color=Allocation), size=5)+
  scale_color_manual(values = col_pal)+
  labs(title = "Arithmetic 30 Year Average Returns: \n Confidence Interval") +
  ylab("Lower Bound") +
  xlab("Allocation (Large Cap)") +
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.75, 0.25),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15))


# 30 yr arithmetic mean vs std
signif_pts0 = signif1_arith_STD_DEV
col_pal <- c(signif_pts0$Rank_Color)
ggplot(data = stats, aes(x = arith_STD_DEV, y = arith_Mean)) + 
  geom_point() + 
  geom_label(data=signif_pts0[3,], aes(x = arith_STD_DEV, y = arith_Mean, 
                                   label = paste0(
                                     "Mean: ", round(arith_Mean, 4), "\n", 
                                     "SD: ", round(arith_STD_DEV, 4))),
             color = "darkgreen", size=4, nudge_x = 0.002) + 
  geom_point(data = signif_pts0, aes(color=Allocation), size=5)+
  scale_color_manual(values = col_pal)+
  labs(title = "Arithmetic 30 Year Average Returns: \n Mean vs. Standard Deviation") +
  ylab("Mean") +
  xlab("Standard Deviation") +
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.75, 0.75),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15))

```




```{r}
# 30 yr arithmetic sharpe1 CI
signif_pts0 = signif_arith_Sharpe1_CI
col_pal <- c(signif_pts0$Rank_Color)
ggplot(data = stats2, aes(x = Spread_num, y = arith_Sharpe1_CI)) + 
  geom_point() + 
  geom_label(data=signif_pts0[2,], aes(x = Spread_num, y = arith_Sharpe1_CI, 
                                   label = paste0(
                                     "95% CI:", "\n", "[", round(arith_Sharpe1_CI, 4), ", ", 
                                     round(arith_Sharpe1_CI2, 4),"]")),
             color = "darkgreen", size=4, nudge_y = -0.03) + 
  geom_point(data = signif_pts0, aes(color=Allocation), size=5)+
  scale_color_manual(values = col_pal)+
  labs(title = "Arithmetic 30 Year Sharpe Ratio (Inflation Adjusted): \n Confidence Interval") +
  ylab("Lower Bound") +
  xlab("Allocation (Large Cap)") +
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.45, 0.25),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15))




# 30 yr arithmetic mean sharpe ratio1
signif_pts0 = signif1_arith_Sharpe1_std
col_pal <- c(signif_pts0$Rank_Color)
ggplot(data = stats, aes(x = arith_Sharpe1_std, y = arith_Sharpe1)) +
  geom_point() +
  geom_label(data=signif_pts0[5,], aes(x = arith_Sharpe1_std, y = arith_Sharpe1,
                                   label = paste0(
                                     "Mean: ", round(arith_Sharpe1, 4), "\n",
                                     "SD: ", round(arith_Sharpe1_std, 4))),
             color = "darkgreen", size=4, nudge_x = 0.03, nudge_y = 0.035) +
  geom_point(data = signif_pts0, aes(color=Allocation), size=5)+
  scale_color_manual(values = col_pal)+
  labs(title = "Arithmetic 30 Year Sharpe Ratio (Inflation Adjusted): \n Mean vs. Standard Deviation") +
  ylab("Mean") +
  xlab("Standard Deviation") +
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.75, 0.275),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15))



# 30 yr arith sharpe2 CI
signif_pts0 = signif_arith_Sharpe2_CI
col_pal <- c(signif_pts0$Rank_Color)
ggplot(data = stats2, aes(x = Spread_num, y = arith_Sharpe2_CI)) + 
  geom_point() + 
  geom_label(data=signif_pts0[3,], aes(x = Spread_num, y = arith_Sharpe2_CI, 
                                   label = paste0(
                                     "95% CI:", "\n", "[", round(arith_Sharpe2_CI, 4), ", ", 
                                     round(arith_Sharpe2_CI2, 4),"]")),
             color = "darkgreen", size=4, nudge_y = -0.04) + 
  geom_point(data = signif_pts0, aes(color=Allocation), size=5)+
  scale_color_manual(values = col_pal)+
  labs(title = "Arithmetic 30 Year Sharpe Ratio: \n Confidence Interval") +
  ylab("Lower Bound") +
  xlab("Allocation (Large Cap)") +
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.45, 0.25),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15))



# 30 yr arith sharpe2
signif_pts0 = signif1_arith_Sharpe2_std
col_pal <- c(signif_pts0$Rank_Color)
ggplot(data = stats, aes(x = arith_Sharpe2_std, y = arith_Sharpe2)) + 
  geom_point() + 
  geom_label(data=signif_pts0[5,], aes(x = arith_Sharpe2_std, y = arith_Sharpe2, 
                                   label = paste0(
                                     "Mean: ", round(arith_Sharpe2, 4), "\n", 
                                     "SD: ", round(arith_Sharpe2_std, 4))),
             color = "darkgreen", size=4, nudge_x = 0.01, nudge_y = -0.02) + 
  geom_point(data = signif_pts0, aes(color=Allocation), size=5)+
  scale_color_manual(values = col_pal)+
  labs(title = "Arithmetic 30 Year Sharpe Ratio: \n Mean vs. Standard Deviation") +
  ylab("Mean") +
  xlab("Standard Deviation") +
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.25, 0.25),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15))
```

```{r}
# 30 yr arithmetic rrr ratio CI
signif_pts0 = signif_Prob
col_pal <- c(signif_pts0$Rank_Color)
ggplot(data = stats2, aes(x = Spread_num, y = Prob)) + 
  geom_point() + 
  geom_label(data=signif_pts0[2,], aes(x = Spread_num, y = Prob, 
                                   label = paste0(100* round(Prob, 4), "%")),
             color = "darkgreen", size=4, nudge_y = -0.05) + 
  geom_point(data = signif_pts0, aes(color=Allocation), size=5)+
  scale_color_manual(values = col_pal)+
  labs(title = "Arithmetic 30 Year Average Return: \n P[Risk Reward Ratio > 1]")+
  ylab("Probability") +
  xlab("Allocation (Large Cap)") +
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.75, 0.75),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15))



# 30 yr arithmetic RRR
signif_pts0 = signif1_arith_RRR_std
col_pal <- c(signif_pts0$Rank_Color)
ggplot(data = stats, aes(x = arith_RRR_std, y = arith_RRR)) + 
  geom_point() + 
  geom_label(data=signif_pts0[2,], aes(x = arith_RRR_std, y = arith_RRR, 
                                   label = paste0(
                                     "Mean: ", round(arith_RRR, 4), "\n", 
                                     "SD: ", round(arith_RRR_std, 4))),
             color = "darkgreen", size=4, nudge_y = 0.12, nudge_x = 0.005) + 
  geom_point(data = signif_pts0, aes(color=Allocation), size=5)+
  scale_color_manual(values = col_pal)+
  labs(title = "Arithmetic 30 Year Average Return Risk Reward Ratio: \n Mean vs. Standard Deviation") +
  ylab("Mean") +
  xlab("Standard Deviation") +
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.25, 0.7),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15))
```


```{r}
# 30 yr Geommtric mean CI
signif_pts0 = signif_Geom_CI
col_pal <- c(signif_pts0$Rank_Color)
ggplot(data = stats2, aes(x = Spread_num, y = Geom_CI)) + 
  geom_point() + 
  geom_label(data=signif_pts0[4,], aes(x = Spread_num, y = Geom_CI, 
                                   label = paste0(
                                     "95% CI:", "\n", "[", round(Geom_CI, 4), ", ", 
                                     round(Geom_CI2, 4),"]")),
             color = "darkgreen", size=4, nudge_y = -0.01, nudge_x = -6) + 
  geom_point(data = signif_pts0, aes(color=Allocation), size=5)+
  scale_color_manual(values = col_pal)+
  labs(title = "Geometric 30 Year Average Returns: \n Confidence Interval") +
  ylab("Lower Bound") +
  xlab("Allocation (Large Cap)") +
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.75, 0.25),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15))



# 30 yr Geometric mean vs std
signif_pts0 = signif1_Geom_STD_DEV
col_pal <- c(signif_pts0$Rank_Color)
ggplot(data = stats, aes(x = Geom_STD_DEV, y = Geom_Mean)) + 
  geom_point() + 
  geom_label(data=signif_pts0[3,], aes(x = Geom_STD_DEV, y = Geom_Mean, 
                                   label = paste0(
                                     "Mean: ", round(Geom_Mean, 4), "\n", 
                                     "SD: ", round(Geom_STD_DEV, 4))),
             color = "darkgreen", size=4, nudge_x = 0.002) + 
  geom_point(data = signif_pts0, aes(color=Allocation), size=5)+
  scale_color_manual(values = col_pal)+
  labs(title = "Geometric 30 Year Average Returns: \n Mean vs. Standard Deviation") +
  ylab("Mean") +
  xlab("Standard Deviation") +
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.75, 0.75),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15))
```


```{r}

# 30 yr Geometric sharpe1 CI
signif_pts0 = signif_Geom_Sharpe1_CI
col_pal <- c(signif_pts0$Rank_Color)
ggplot(data = stats2, aes(x = Spread_num, y = Geom_Sharpe1_CI)) + 
  geom_point() + 
  geom_label(data=signif_pts0[3,], aes(x = Spread_num, y = Geom_Sharpe1_CI, 
                                   label = paste0(
                                     "95% CI:", "\n", "[", round(Geom_Sharpe1_CI, 4), ", ", 
                                     round(Geom_Sharpe1_CI2, 4),"]")),
             color = "darkgreen", size=4, nudge_y = -0.01) + 
  geom_point(data = signif_pts0, aes(color=Allocation), size=5)+
  scale_color_manual(values = col_pal)+
  labs(title = "Geometric 30 Year Sharpe Ratio (Inflation Adjusted): \n Confidence Interval") +
  ylab("Lower Bound") +
  xlab("Allocation (Large Cap)") +
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.45, 0.25),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15))



# 30 yr Geometric mean sharpe ratio1
signif_pts0 = signif1_Geom_Sharpe1_std
col_pal <- c(signif_pts0$Rank_Color)
ggplot(data = stats, aes(x = Geom_Sharpe1_std, y = Geom_Sharpe1)) +
  geom_point() +
  geom_label(data=signif_pts0[3,], aes(x = Geom_Sharpe1_std, y = Geom_Sharpe1,
                                   label = paste0(
                                     "Mean: ", round(Geom_Sharpe1, 4), "\n",
                                     "SD: ", round(Geom_Sharpe1_std, 4))),
             color = "darkgreen", size=4, nudge_x = 0.0005) +
  geom_point(data = signif_pts0, aes(color=Allocation), size=5)+
  scale_color_manual(values = col_pal)+
  labs(title = "Geometric 30 Year Sharpe Ratio (Inflation Adjusted): \n Mean vs. Standard Deviation") +
  ylab("Mean") +
  xlab("Standard Deviation") +
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.75, 0.3),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15))


# 30 yr Geometric sharpe2 CI
signif_pts0 = signif_Geom_Sharpe2_CI
col_pal <- c(signif_pts0$Rank_Color)
ggplot(data = stats2, aes(x = Spread_num, y = Geom_Sharpe2_CI)) + 
  geom_point() + 
  geom_label(data=signif_pts0[3,], aes(x = Spread_num, y = Geom_Sharpe2_CI, 
                                   label = paste0(
                                     "95% CI:", "\n", "[", round(Geom_Sharpe2_CI, 4), ", ", 
                                     round(Geom_Sharpe2_CI2, 4),"]")),
             color = "darkgreen", size=4, nudge_y = -0.05) + 
  geom_point(data = signif_pts0, aes(color=Allocation), size=5)+
  scale_color_manual(values = col_pal)+
  labs(title = "Geometric 30 Year Sharpe Ratio: \n Confidence Interval") +
  ylab("Lower Bound") +
  xlab("Allocation (Large Cap)") +
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.45, 0.25),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15))



# 30 yr Geom sharpe2
signif_pts0 = signif1_Geom_Sharpe2_std
col_pal <- c(signif_pts0$Rank_Color)
ggplot(data = stats, aes(x = Geom_Sharpe2_std, y = Geom_Sharpe2)) + 
  geom_point() + 
  geom_label(data=signif_pts0[5,], aes(x = Geom_Sharpe2_std, y = Geom_Sharpe2, 
                                   label = paste0(
                                     "Mean: ", round(Geom_Sharpe2, 4), "\n", 
                                     "SD: ", round(Geom_Sharpe2_std, 4))),
             color = "darkgreen", size=4, nudge_x = 0.01, nudge_y = -0.025) + 
  geom_point(data = signif_pts0, aes(color=Allocation), size=5)+
  scale_color_manual(values = col_pal)+
  labs(title = "Geometric 30 Year Sharpe Ratio: \n Mean vs. Standard Deviation") +
  ylab("Mean") +
  xlab("Standard Deviation") +
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.45, 0.25),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15))
```


```{r}

signif_pts0 = signif_Prob2
col_pal <- c(signif_pts0$Rank_Color)
ggplot(data = stats2, aes(x = Spread_num, y = Prob2)) + 
  geom_point() + 
  geom_label(data=signif_pts0[2,], aes(x = Spread_num, y = Prob2, 
                                   label = paste0(100* round(Prob2, 4), "%")),
             color = "darkgreen", size=4, nudge_y = -0.05) + 
  geom_point(data = signif_pts0, aes(color=Allocation), size=5)+
  scale_color_manual(values = col_pal)+
  labs(title = "Geometric 30 Year Average Return: \n P[Risk Reward Ratio > 1]")+
  ylab("Probability") +
  xlab("Allocation (Large Cap)") +
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.75, 0.75),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15))


# 30 yr Geometric RRR
signif_pts0 = signif1_Geom_RRR_std
col_pal <- c(signif_pts0$Rank_Color)
ggplot(data = stats, aes(x = Geom_RRR_std, y = Geom_RRR)) + 
  geom_point() + 
  geom_label(data=signif_pts0[2,], aes(x = Geom_RRR_std, y = Geom_RRR, 
                                   label = paste0(
                                     "Mean: ", round(Geom_RRR, 4), "\n", 
                                     "SD: ", round(Geom_RRR_std, 4))),
             color = "darkgreen", size=4, nudge_y = 0.12, nudge_x = 0.01) + 
  geom_point(data = signif_pts0, aes(color=Allocation), size=5)+
  scale_color_manual(values = col_pal)+
  labs(title = "Geometric 30 Year Average Return Risk Reward Ratio: \n Mean vs. Standard Deviation") +
  ylab("Mean") +
  xlab("Standard Deviation") +
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.25, 0.75),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15))
```


```{r}
# 30 yr total compounded returns  CI
signif_pts0 = signif_Total_Return_CI
col_pal <- c(signif_pts0$Rank_Color)
ggplot(data = stats2, aes(x = Spread_num, y = Total_Return_CI)) + 
  geom_point() + 
  geom_label(data=signif_pts0[3,], aes(x = Spread_num, y = Total_Return_CI, 
                                   label = paste0(
                                     "95% CI:", "\n", "[", round(Total_Return_CI, 4), ", ", 
                                     round(Total_Return_CI2, 4),"]")),
             color = "darkgreen", size=4, nudge_y = -1) + 
  geom_point(data = signif_pts0, aes(color=Allocation), size=5)+
  scale_color_manual(values = col_pal)+
  labs(title = "Compounded 30 Year Average Returns: \n Confidence Interval") +
  ylab("Lower Bound") +
  xlab("Allocation (Large Cap)") +
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.75, 0.25),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15))


# 30 yr cmpd mean vs std
signif_pts0 = signif1_Total_Return_std
col_pal <- c(signif_pts0$Rank_Color)
ggplot(data = stats, aes(x = Total_Return_std, y = Total_Return)) + 
  geom_point() + 
  geom_label(data=signif_pts0[1,], aes(x = Total_Return_std, y = Total_Return, 
                                   label = paste0("Mean: ", round(Total_Return, 4), "\n", 
                                     "SD: ", round(Total_Return_std, 4))),
             color = "darkgreen", size=4, nudge_x = 1, nudge_y = 0.5) + 
  geom_point(data = signif_pts0, aes(color=Allocation), size=5)+
  scale_color_manual(values = col_pal)+
  labs(title = "Annually Compounded 30 Year Average Returns: \n Mean vs. Standard Deviation") +
  ylab("Mean") +
  xlab("Standard Deviation") +
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.75, 0.25),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15))

```


```{r}
# 30 yr cmpd sharpe1 CI
signif_pts0 = signif_Total_Sharpe1_CI
col_pal <- c(signif_pts0$Rank_Color)
ggplot(data = stats2, aes(x = Spread_num, y = Total_Sharpe1_CI)) + 
  geom_point() + 
  geom_label(data=signif_pts0[4,], aes(x = Spread_num, y = Total_Sharpe1_CI, 
                                   label = paste0(
                                     "95% CI:", "\n", "[", round(Total_Sharpe1_CI, 4), ", ", 
                                     round(Total_Sharpe1_CI2, 4),"]")),
             color = "darkgreen", size=4, nudge_y = -0.0015) + 
  geom_point(data = signif_pts0, aes(color=Allocation), size=5)+
  scale_color_manual(values = col_pal)+
  labs(title = "Compounded 30 Year Sharpe Ratio (Inflation Adjusted): \n Confidence Interval") +
  ylab("Lower Bound") +
  xlab("Allocation (Large Cap)") +
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.75, 0.25),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15))



# 30 yr compounded returns sharpe ratio1
signif_pts0 = signif1_Total_Sharpe1_std
col_pal <- c(signif_pts0$Rank_Color)
ggplot(data = stats, aes(x = Total_Sharpe1_std, y = Total_Sharpe1)) +
  geom_point() +
  geom_label(data=signif_pts0[2,], aes(x = Total_Sharpe1_std, y = Total_Sharpe1,
                                   label = paste0(
                                     "Mean: ", round(Total_Sharpe1, 4), "\n",
                                     "SD: ", round(Total_Sharpe1_std, 4))),
             color = "darkgreen", size=4, nudge_x = 0.0005) +
  geom_point(data = signif_pts0, aes(color=Allocation), size=5)+
  scale_color_manual(values = col_pal)+
  labs(title = "Compounded 30 Year Sharpe Ratio (Inflation Adjusted): \n Mean vs. Standard Deviation") +
  ylab("Mean") +
  xlab("Standard Deviation") +
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.75, 0.5),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15))


# 30 yr cmpd sharpe2 CI
signif_pts0 = signif_Total_Sharpe2_CI
col_pal <- c(signif_pts0$Rank_Color)
ggplot(data = stats2, aes(x = Spread_num, y = Total_Sharpe2_CI)) + 
  geom_point() + 
  geom_label(data=signif_pts0[3,], aes(x = Spread_num, y = Total_Sharpe2_CI, 
                                   label = paste0(
                                     "95% CI:", "\n", "[", round(Total_Sharpe2_CI, 4), ", ", 
                                     round(Total_Sharpe2_CI2, 4),"]")),
             color = "darkgreen", size=4, nudge_y = -0.005) + 
  geom_point(data = signif_pts0, aes(color=Allocation), size=5)+
  scale_color_manual(values = col_pal)+
  labs(title = "Compounded 30 Year Sharpe Ratio: \n Confidence Interval") +
  ylab("Lower Bound") +
  xlab("Allocation (Large Cap)") +
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.75, 0.25),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15))



# 30 yr cmpd sharpe2
signif_pts0 = signif1_Total_Sharpe2_std
col_pal <- c(signif_pts0$Rank_Color)
ggplot(data = stats, aes(x = Total_Sharpe2_std, y = Total_Sharpe2)) + 
  geom_point() + 
  geom_label(data=signif_pts0[3,], aes(x = Total_Sharpe2_std, y = Total_Sharpe2, 
                                   label = paste0(
                                     "Mean: ", round(Total_Sharpe2, 4), "\n", 
                                     "SD: ", round(Total_Sharpe2_std, 4))),
             color = "darkgreen", size=4, nudge_x = 0.0003, nudge_y = -0.003) + 
  geom_point(data = signif_pts0, aes(color=Allocation), size=5)+
  scale_color_manual(values = col_pal)+
  labs(title = "Compounded 30 Year Sharpe Ratio: \n Mean vs. Standard Deviation") +
  ylab("Mean") +
  xlab("Standard Deviation") +
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.75, 0.75),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15))


```


```{r}
# 30 yr cmpd RRR
signif_pts0 = signif_Total_RRR_CI
col_pal <- c(signif_pts0$Rank_Color)
ggplot(data = stats2, aes(x = Spread_num, y = Total_RRR_CI)) + 
  geom_point() + 
  geom_label(data=signif_pts0[2,], aes(x = Spread_num, y = Total_RRR_CI, 
                                   label = paste0(
                                     "95% CI:", "\n", "[", round(Total_RRR_CI, 4), ", ", 
                                     round(Total_RRR_CI2, 4),"]")),
             color = "darkgreen", size=4, nudge_y = -0.002) + 
  geom_point(data = signif_pts0, aes(color=Allocation), size=5)+
  scale_color_manual(values = col_pal)+
  labs(title = "Compounded 30 Year Average Return Risk Reward Ratio: \n Confidence Interval")+
  ylab("Lower Bound") +
  xlab("Allocation (Large Cap)") +
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.75, 0.25),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15))


# 30 yr cmpd RRR
signif_pts0 = signif1_Total_RRR_std
col_pal <- c(signif_pts0$Rank_Color)
ggplot(data = stats, aes(x = Total_RRR_std, y = Total_RRR)) + 
  geom_point() + 
  geom_label(data=signif_pts0[2,], aes(x = Total_RRR_std, y = Total_RRR, 
                                   label = paste0(
                                     "Mean: ", round(Total_RRR, 4), "\n", 
                                     "SD: ", round(Total_RRR_std, 4))),
             color = "darkgreen", size=4, nudge_y = 0.00005, nudge_x = 0.0007) + 
  geom_point(data = signif_pts0, aes(color=Allocation), size=5)+
  scale_color_manual(values = col_pal)+
  labs(title = "Compounded 30 Year Average Return Risk Reward Ratio: \n Mean vs. Standard Deviation") +
  ylab("Mean") +
  xlab("Standard Deviation") +
  theme(plot.title = element_text(hjust = 0.5, size =18),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=15),
        legend.position = c(0.75, 0.5),
        legend.text = element_text(size=12),
        legend.title = element_text(size=15))

```